### 2015-02-12 src/misc/s1_intro.tex
Minor updates

Life began about four billion years ago with the encapsulation of self-replicating RNA in a lipidic membrane (e.g. Orgel, 2004). Simple as these probionts were, they did not have any means of locomotion and thus relied in full on the currents to deliver nutrients required to replicate.

@@

\section{Sensory signals}
While many sensory organs supply information used in navigation, there is one system that evolved specifically for this purpose: the vestibular system. Its two components, the semicircular canals and the otoliths, are housed in the labyrinth of the temporal bone in the inner ear and are sensitive to angular and linear acceleration respectively.

@@

\subsubsection{Semicircular canals}
The semicircular canals measure rotational acceleration of the head. Each of the six  canals consists of a circular tube filled with a fluid known as endolymph (see Figure ?A). One part of the tube, the ampulla, is a bit thicker than the rest and contains a membrane, the cupula, that separates the fluid. When the head rotates, the fluid stays behind because of its inertia which in turn causes the membrane to deflect (see Figure ?B). Special hair cells, partly embedded in the cupula, measure this deflection and thus rotational acceleration.

@@

@@

Because gravity also affects the otoconia, the vertically oriented ones are always deflected downward. It is therefore impossible to differentiate the linear acceleration from gravity based on the otolith signal alone. While various theories have been proposed to differentiate these stimuli, recent research favours the canal-otolith interaction theory as first proposed by Merfield and Zupan (year). In short, they state that the relative canal signal is used to update the direction of gravity and that this estimate of gravity is then subtracted from the otolith signal in order to obtain an estimate for linear accleration.

@@

\subsection{Somatosensory}
The gravito-intertial force caused by gravity or acceleration influences not only the vestibular system, but all other organs as well and can thus be used for both perception and action. The first evidence that these effects were used by the brain came from DeKleyn and Versteegh (1933) who showed that intertial reflexes still occurred after removal of the otolith organs.

Since then, the contribution of specific organs to GIF perception has been demonstrated. When the stomach is full, for example, performance on the subjective visual vertical (SVV) task, that is orienting a visual line with gravity, improves compared to when it's empty. This suggests that signals from the stomach are used in the perception of vertical (Trousselard et al., 2004). Furtermore, SVV performance was shown to decrease when a body-cast was applied. As the cast attentuates skin pressure, this result suggests that skin pressure is also an important cue (Trousselard et al., 2004). Similar results were obtained for many other organs, such as the blood vessels (Vaitl, 2002), kidneys and spinal axis fluid (Vailt et al., 1997).

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retinae shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (Figure XA) for example causes a different pattern from roll rotation (Figure XB). At the turn of the 19th century von Helmholz (1910) recognized the importance of these flow signals for self-motion perception and Gibson (1950) formalized the concept.

Gibson? What did he show?

Similar retinal shifts are also observed during movement of the eyes or head as well as motion of the environment. When parsing optic flow the brain needs to distinguish object- from self-motion.

[TRAIN EXAMPLE? This section still needs a lot of work]

[Figure XA: Vection pattern in lateral translation; XB: Vection pattern in rotation]

\subsubsection{Landmarks}
In addition to relative cues, the brain also uses absolute cues in both the perception of gravity as well as our location, and thus displacement. For the perception of gravity, it makes use of the factthat many lines within the world are aligned with either the horizon or gravity. Any straight line close therefore acts as a prior attracting the perceived direction of gravity torwards it (see Figure XA). Similarly, our absolute position within the world can be established using world-fixed landmarks. With the exception of animals and vehicles, most items in the world rarely change position. By comparing our current visual scene (e.g. the Arc-du-Triomph tower) with our knowledge of the enviroment we can determine our location (in this case Paris, see Figure XB). Because the experiments outlined in this thesis were performed in near darkness, these absolute  navigational cues are less relevant. [Could it be that the fixation target is a world-fixed reference? Add something about that here or later.]

[Rod and frame illusion?]

[Figure XA: Image of Arc de Triomph with vertical lines; XB: Map of paris, likely location]

\subsubsection{Oculomotor}
While retinal information plays an important role in orientation and navigation, other, extra-retinal, visual signals are also informative. Eye movements, for example, are known to increase postural sway in darkness (Glasauer, et al., 2005). The increased sway is likely compensation for perceived self-motion caused by these eye movements. Such percept could be a remnant of optic flow processing, even though there is no optic flow in darkness, the eye movement signal still reaches the neural network responsible for compensating optic flow for eye movements and as such leak into self-motion perception. Evidence for this can be found in the fact that postural sway decreases when a stable background is presented (Glasauer et al., 2005; Rodrigues et al., 2015), where the  flow during eye movements balances the eye movement signal itself.

@@

As these VOR compensate for both rotation as well as translation, the VOR consists of two reflex arcs. The translational VOR, or TVOR, is driven by the otolith signal while the rotational VOR, or RVOR, is mainly driven by the semicircular canals. Unlike the visual system, the vestibular system does not require elaborate processing in order to drive the reflexive eye movements. Because of this, the reflex arc reaches the oculomotor system in just three neural links. This greatly reduces the latency of the VOR compared to that of the OKR and causes the VOR to dominate at higher frequencies (Schweigard et al., 1997).

@@

In conflicting situations where visual cues contradict vestibular and proprioceptive ones a dominance of vision is observed (Berthoz, Pavard, Young, 1975).

In contrast, linear acceleration can change the perceived velocity of a moving visual scene, indicaing dominance of the vestibular over the visual signal (Pavard, Berthoz, 1977). Mainly at low image velocities! At high image velocities the visual signal still dominates.

@@

The two-alternative forced choice, or 2AFC, paradigm is commonly used in psychophyiscal experiments. Participants are presented with two stimuli, e.g. two translation distances, and are then forced to make a choice, e.g. on which of the translations was longer. By structurally manipulating one of the choices the point of subjective equality, or PSE, can be determined, that is the point at which the participant is unsure, i.e. picks a response at random, and perceives the stimuli as being equal. The difference between the PSE and the actual stimulus is known as the bias, represented by the Greek letter mu (μ)..

In addition to establishing perceptual equality, the uncertainty on the responses can also be determined by looking at the response-distribution as a function of the manipulated variable. This uncertainty is commonly quantified by the standard deviation, represented by the Greek letter sigma (σ).

@@

\subsection{Subjective body tilt}
In the subjective body tilt, or SBT, task the perceived body orientation with respect to a given body tilt angle is probed. Participants are first given a reference ange, e.g. 450, and are then rotated to an angle close to the reference angle, e.g. 460 (see Figure XA). They then have to indicate whether their current orientation is clockwise or counterclockwise with respect to the reference angle. By systematically probing rotation angles around the reference angle we can obtain both the bias and uncertainty on the percept of body tilt.

Most participants are able to do this perfectly, regardless of the reference angle (see Figure XB). Their uncertainty does increase as a function of reference angle though (see Figure XC).
As the SBT probes body orientation, the somatosensory signal originating from the torso can be used without any reference transformation and thus provides a direct contriubtion. Other sensory signals such as the vestibular signal can also be used, but only after a reference frame transformation.

\subsection{Subjective visual vertical}
The subjective visual vertical, or SVV, task is a similar task in which participants have to judge the orientation of a line with respect to gravity. The PSE, that is the angle at which the line is perceived to be aligned with gravity, can be found by presenting lines at different angles and asking the participant whether the line is rotated clockwise or counterclockwise relative to gravity (see Figure XA).

When seated straight this task, participants do not make any static errors and are very certain about their responses (see Figure XB and C). This changes when first rotating the participant before the task. In general, the static error increases with tilt angle, the direction of the error is in the direction of the body midline, this effect is known as the Aubert or A-effect. At smaller angles overcompensation occurs and the static error moves in the oposite direction, that is away from the body midline. This latter effect is known as the E-effect and could be due to the effects of ocular counterroll (OCR).

>>>>

Life began about four billion years ago with the encapsulation of self-replicating RNA in a lipidic membrane \cite<e.g.>{orgel1968}. Simple as these probionts were, they did not have any means of locomotion and thus relied in full on the currents to deliver nutrients required to replicate.

@@

\section{Sensory signals}
While many sensory organs supply information used in navigation, there is one system that evolved specifically for this purpose: the vestibular system (see \figref{intro:fig6}). Its two components, the semicircular canals and the otoliths, are housed in the labyrinth of the temporal bone in the inner ear and are sensitive to angular and linear acceleration respectively.

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/misc/figures/Vestibular.png}
    \caption{Schematic view of the inner ear complex consisting of the auditory system (cochlea) and the vestibular system. The vestibular system has three angular velocity (semicircular canals) and two linear acceleration (saccule and utricle) sensors.}
    \label{intro:fig6}
\end{figure}

\subsubsection{Semicircular canals}
The semicircular canals measure rotational acceleration of the head. Each of the six  canals consists of a circular tube filled with a fluid known as endolymph (see \figref{intro:fig3}A). One part of the tube, the ampulla, is a bit thicker than the rest and contains a membrane, the cupula, that separates the fluid. When the head rotates, the fluid stays behind because of its inertia which in turn causes the membrane to deflect (see \figref{intro:fig3}B). Special hair cells, partly embedded in the cupula, measure this deflection and thus rotational acceleration.

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/misc/figures/Canals.png}
    \caption{Detailed view of a semicircular canal \panelref{A} in rest and \panelref{B} during rotation. Inertia of the endolymph in the canal causes the cupula to deflect during rotation.}
    \label{intro:fig3}
\end{figure}

@@

Because gravity also affects the otoconia, the vertically oriented ones are always deflected downward. It is therefore impossible to differentiate the linear acceleration from gravity based on the otolith signal alone. While various theories have been proposed to differentiate these stimuli, recent research favours the canal-otolith interaction theory as first proposed by Merfield and Zupan \textbf{(check the year)}. In short, they state that the relative canal signal is used to update the direction of gravity and that this estimate of gravity is then subtracted from the otolith signal in order to obtain an estimate for linear accleration.

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/misc/figures/Otoliths.png}
    \caption{Detailed view of an otolith \panelref{A} in rest, \panelref{B} during head tilt, and \panelref{C} during linear acceleration. The high inertia of the otoconia keeps them from moving rapidly during both head tilt as well as linear acceleration. As the effect is physically identical in either case, head tilt and linear acceleration cannot be disambiguated based on the otolith signal alone.}
    \label{intro:fig7}
\end{figure}

\subsection{Somatosensory}
The gravito-intertial force caused by gravity or acceleration influences not only the vestibular system, but all other organs as well and can thus be used for both perception and action. The first evidence that these effects were used by the brain came from DeKleyn and Versteegh \citeyear{dekleyn1933} who showed that intertial reflexes still occurred after removal of the otolith organs.

Since then, the contribution of specific organs to GIF perception has been demonstrated. When the stomach is full, for example, performance on the subjective visual vertical (SVV) task, that is orienting a visual line with gravity, improves compared to when it's empty. This suggests that signals from the stomach are used in the perception of vertical \cite{trousselard2004}. Furtermore, SVV performance was shown to decrease when a body-cast was applied. As the cast attentuates skin pressure, this result suggests that skin pressure is also an important cue \cite{trousselard2004}. Similar results were obtained for many other organs, such as the blood vessels \cite{vaitl2002}, kidneys and spinal axis fluid \cite{vaitl1997}.

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retina shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (\figref{intro:fig2}A) for example causes a different pattern from roll rotation (\figref{intro:fig2}B). At the turn of the 19th century von Helmholz \citeyear{vonhelmholz1910} recognized the importance of these flow signals for self-motion perception. In some cases the vection signal is so strong, it causes a percept of self-motion in stationary participants. This happens, for example, when sitting in a train and the neighboring train starts to move. This effect is much less likely to occur when e.g. on the platform, suggesting that the vection signal is integrated with prior knowledge about the environment before causing self-motion perception (reference).

Similar retinal shifts are also observed during movement of the eyes or head as well as motion of the environment. When interpreting optic flow the brain needs to distinguish object- from self-motion.

% MORE ABOUT DISTINGUISHING OBJECT FROM SELF-MOTION

\begin{figure}
    %\includegraphics[width=1.0\textwidth]{src/misc/figures/Vection.pdf}

    \caption{Vection pattern during \panelref{A} lateral translation and \panelref{B} rotation.}
    \label{intro:fig2}
\end{figure}

\subsubsection{Landmarks}
In addition to relative cues, the brain also uses absolute cues in both the perception of gravity as well as our location, and thus displacement. For the perception of gravity, it makes use of the fact that many lines within the world are aligned with either the horizon or gravity. Straight lines therefore acts as a priors attracting the perceived direction of gravity torwards them. A special case is the rod-and-frame illusion (\figref{intro:fig9}), where the perceived angle of a rod relative to gravity is affected by the orientation of the frame that contains it (reference).

\begin{figure}
	%\includegraphics[width=1.0\textwidth]{src/misc/figures/RodFrame.pdf}
	\caption{..}
	\label{intro:fig9}
\end{figure}

Similarly, our absolute position within the world can be established using world-fixed landmarks. With the exception of animals and vehicles, most items in the world rarely change position. By comparing our current visual scene (e.g. \figref{intro:fig1}) with our knowledge of the enviroment we can determine our location (in this case Grand Canyon). Because the experiments outlined in this thesis were performed in near darkness, these absolute  navigational cues are less relevant.

% Why not use redwood forest instead? It has lots of vertical trees.
\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/misc/figures/Canyon.pdf}

    \caption{While the scene in the left panel might not give precise information about your location in the world, it does narrow it down to somewhere in the vicinity of the Grand Canyon (right panel). In addition, the horizon in the scene gives information about the orientation of the horizontal plane and thus about the orientation of the viewer with respect to gravity. \copyright Mojan Brenn}
    \label{intro:fig1}
\end{figure}

\subsubsection{Oculomotor}
While retinal information plays an important role in orientation and navigation, other, extra-retinal, visual signals are also informative. Eye movements, for example, are known to increase postural sway in darkness \cite{glasauer2005}. The increased sway is likely compensation for perceived self-motion caused by these eye movements. Such percept could be a remnant of optic flow processing, even though there is no optic flow in darkness, the eye movement signal still reaches the neural network responsible for compensating optic flow for eye movements and as such leak into self-motion perception. Evidence for this can be found in the fact that postural sway decreases when a stable background is presented \cite{glasauer2005,rodrigues2015}, where the  flow during eye movements balances the eye movement signal itself.

@@

As these VOR compensate for both rotation as well as translation, the VOR consists of two reflex arcs. The translational VOR, or TVOR, is driven by the otolith signal while the rotational VOR, or RVOR, is mainly driven by the semicircular canals. Unlike the visual system, the vestibular system does not require elaborate processing in order to drive the reflexive eye movements. Because of this, the reflex arc reaches the oculomotor system in just three neural links. This greatly reduces the latency of the VOR compared to that of the OKR and causes the VOR to dominate at higher frequencies \cite{schweigard1997}.

@@

In conflicting situations where visual cues contradict vestibular and proprioceptive ones a dominance of vision is observed \cite{berthoz1975}.

In contrast, linear acceleration can change the perceived velocity of a moving visual scene, indicaing dominance of the vestibular over the visual signal \cite{pavard1977}. Mainly at low image velocities! At high image velocities the visual signal still dominates.

@@

The two-alternative forced choice, or 2AFC, paradigm is commonly used in psychophyiscal experiments. Participants are presented with two stimuli, e.g. two translation distances, and are then forced to make a choice, e.g. on which of the translations was longer. By structurally manipulating one of the choices the point of subjective equality, or PSE, can be determined, that is the point at which the participant is unsure, i.e. picks a response at random, and perceives the stimuli as being equal. The difference between the PSE and the actual stimulus is known as the bias, represented by the Greek letter mu ($\mu$).

In addition to establishing perceptual equality, the uncertainty on the responses can also be determined by looking at the response-distribution as a function of the manipulated variable. This uncertainty is commonly quantified by the standard deviation, represented by the Greek letter sigma ($\sigma$).

@@

\subsection{Subjective body tilt}
In the subjective body tilt, or SBT, task the perceived body orientation with respect to a given body tilt angle is probed. Participants are first given a reference ange, e.g. 45 \si{\degree}, and are then rotated to an angle close to the reference angle, e.g. 46 \si{\degree} (see \figref{intro:fig4}A). They then have to indicate whether their current orientation is clockwise or counterclockwise with respect to the reference angle. By systematically probing rotation angles around the reference angle we can obtain both the bias and uncertainty on the percept of body tilt.

Most participants are able to do this perfectly, regardless of the reference angle (see \figref{intro:fig4}B). Their uncertainty does increase as a function of reference angle though (see \figref{intro:fig4}C).
As the SBT probes body orientation, the somatosensory signal originating from the torso can be used without any reference transformation and thus provides a direct contriubtion. Other sensory signals such as the vestibular signal can also be used, but only after a reference frame transformation.

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/misc/figures/SBT.png}

    \caption{}
    \label{intro:fig4}
\end{figure}

\subsection{Subjective visual vertical}
The subjective visual vertical, or SVV, task is a similar task in which participants have to judge the orientation of a line with respect to gravity. The PSE, that is the angle at which the line is perceived to be aligned with gravity, can be found by presenting lines at different angles and asking the participant whether the line is rotated clockwise or counterclockwise relative to gravity (see \figref{intro:fig5}A).

When seated straight this task, participants do not make any static errors and are very certain about their responses (see \figref{intro:fig5}B and C). This changes when first rotating the participant before the task. In general, the static error increases with tilt angle, the direction of the error is in the direction of the body midline, this effect is known as the Aubert or A-effect. At smaller angles overcompensation occurs and the static error moves in the oposite direction, that is away from the body midline. This latter effect is known as the E-effect and could be due to the effects of ocular counterroll (OCR).

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/misc/figures/SVV.png}

    \caption{}
    \label{intro:fig5}
\end{figure}

### 2015-02-12 src/misc/s2_discussion.tex
Minor updates

Based on our updating and self-motion perception studies -> is it possible to make predictions for other studies?
What would we predict van Pelt would do for instance?
+
Could check Anna/Alexandra results again -> updating + self-motion effect.

>>>>

%%%%%%%%%%
% Introduction

\section{Summary}

%%%%%%%%%%%%%
% The idea is to concatenate the abstracts for all papers
% and then smoothen the text out a bit.
% Look at what Frank and Verena did in their Theses.

% 1st paper in thesis
Most evidence that the brain uses Bayesian inference to integrate noisy sensory signals optimally has been obtained by showing that the noise levels in each modality separately can predict performance in combined conditions. Such a forward approach is difficult to implement when the various signals cannot be measured in isolation, as in spatial orientation, which involves the processing of visual, somatosensory, and vestibular cues. Instead, we applied an inverse probabilistic approach, based on optimal observer theory. Our goal was to investigate whether the perceptual differences found when probing two different states ---body-in-space and head-in-space orientation--- can be reconciled by a shared scheme using all available sensory signals. Using a psychometric approach, seven human subjects were tested on two orientation estimates at tilts \textless 120\textdegree: perception of body tilt [subjective body tilt (SBT)] and perception of visual vertical [subjective visual vertical (SVV)]. In all subjects, the SBT was more accurate than the SVV, which showed substantial systematic errors for tilt angles beyond 60\textdegree. Variability increased with tilt angle in both tasks, but was consistently lower in the SVV. The sensory integration model fitted both datasets very nicely. A further experiment, in which supine subjects judged their head orientation relative to the body, independently confirmed the predicted head-on-body noise by the model. Model predictions based on the derived noise properties from the various modalities were also consistent with previously published deficits in vestibular and somatosensory patients. We conclude that Bayesian computations can account for the typical differences in spatial orientation judgments associated with different task requirements.

% 2nd paper in thesis
Self-motion is typically accompanied by compensatory eye movements that help minimize retinal slip and maximize dynamic visual acuity. To date, it is unknown whether these eye movements also have a reversed role, serving as a cue for self-motion perception. To address this question, we had participants ($n=8$) judge self-motion during different eye movement conditions in the absence of full-field optic flow.  In a 2-AFC task, participants indicated whether the second of two successive, passive, lateral whole-body translations was longer or shorter than the first. Eye movements during each translation were world-stationary, body-stationary or free in an otherwise dark room. Results show that the perceived translations were shorter with body-fixed gaze compared to world-fixed gaze. Using a linear model, we estimated the vestibular and eye movement contributions to self-motion perception and found that eye movement signals contribute approximately 25 percent. The model was validated independently by predicting the effects of eye movements on self-motion perception during the free eye movement conditions, taking the inter-subject variation in oculomotor weight and eye movement patterns into account. We conclude that eye movement signals influence self-motion perception, even in the absence of visual stimulation, and even when oculomotor and vestibular estimates are in conflict, e.g. during body-fixed gaze. We hypothesize that adverse consequences of this seemingly inflexible arrangement are minimal under natural conditions because eye movements and self-motion are highly correlated, and because eye movements are most often accompanied by veridical optic flow cues to self-motion.

% 3rd paper in thesis (see paper 4)

% 4th paper in thesis
In order to maintain visual stability during self-motion, the brain needs to update any ego-centric spatial representations of the environment. Here, we use a novel psychophysical approach to investigate how, and to which extent, the brain integrates visual, extraocular, and vestibular signals pertaining to this spatial update. Participants were oscillated sideways at a frequency of 0.63 Hz while keeping gaze fixed on a stationary light. When the motion direction changed, a reference target was shown either in front or behind the fixation point. At the next reversal, half a cycle later, we tested updating of this reference location by asking participants to judge whether a briefly flashed probe was shown to the left or right of the memorized target. We show that updating is not only biased, but that the direction and magnitude of this bias depend on both gaze and object location, implying that a gaze-centered reference frame is involved. Using geometric modeling, we further show that the gaze-dependent errors can be caused by an underestimation of translation amplitude, by a bias of visually perceived objects towards the fovea (i.e., a foveal bias), or by a combination of both.

\section{Discussion}

%[Could it be that the fixation target is a world-fixed reference? Add something about that here or later.]

%%%%%%%%%%%%%
% Integrated model

Could check Anna/Alexandra results again -> updating + self-motion effect.
Reaching poster I've made for SfN

%%%%%%%%%%%%%%
% Relation to other studies

Based on our updating and self-motion perception studies -> is it possible to make predictions for other studies?
What would we predict van Pelt would do for instance?

%%%%%%%%%%%%%%
% Conclusion

### 2015-02-12 src/paper4/p4_discussion.tex
Minor updates

% Relation to the VOR
Because the function of the LVOR is to keep the eyes stable in the world during linear translation (reference), it also needs to scale with fixation depth \cite{paige1989, busettini1994,paige1998}. It is therefore possible that both the LVOR and self-motion perception use the same signal. Because of the visual fixation point, visual following mechanisms may augment the LVOR compensation. If the oculomotor signal generated by the LVOR is the same signal that is used for self-motion perception, one would expect that the LVOR compensation at 50 and 200cm closely relate to the corresponding oculomotor weights in the present study (see \figref{p4:fig5} and \tabref{p4:tab2}).

% WARNING, WE LOOK AT D200/D50 in the FIGURE!

We first computed the expected LVOR compensation based

The ratio of the 5.6 and 3.0 \textdegree LVOR compensation at the 50 and 200cm distances, as extrapolated from Paige \citeyear{1989}, is 1.87.

We took the LVOR compensation, as extrapolated from Paige \citeyear{paige1989}, at the 50 and 200cm distances and

We compared the gain found by Paige \citeyear{paige1989}

We extrapolated the gains found by Paige \citeyear{paige1989} to the 50 and 200cm fixation distances in our experiment and found gains of 0.50 and 0.68 respectively.

The expected LVOR compensation based on these gains is 5.6 and 3.0 degrees for near and far fixation respectively. The ratio, 1.87, does not match either the 6 participants who do not show any sign of scaling ($\frac{d_{200}}{d_{50}} = 1.07 \pm 0.16$) or the 2 that do ($\frac{d_{200}}{d_{50}} = 3.06 \pm 0.27$), but does match the overall overage of  1.56 \textpm 0.35.

% Talk about whether perception and action employ different mechanisms?
% Check work by Merfeld
%
% Vestibular perception and action employ qualitatively different mechanisms I and II
% Merfeld, Park, Gianna-Pulin, Black, Wood, 2005
%

>>>>

% Relation to the VOR
Because the function of the LVOR is to keep the eyes stable in the world during linear translation (reference), it also needs to scale with fixation depth \cite{paige1989, busettini1994,paige1998}. It is therefore possible that both the LVOR and self-motion perception use the same signal. Because of the visual fixation point, visual following mechanisms may augment the LVOR compensation. If the oculomotor signal generated by the LVOR is the same signal that is used for self-motion perception, one would expect that the LVOR compensation at 50 and 200cm closely relate to the corresponding oculomotor weights in the present study (see \figref{p4:fig5} and \tabref{p4:tab2}). We computed the expected distance ratio, $d_{200} / d_{50}$, based on the predicted LVOR eye movements for our viewing distances as extrapolated from Paige \citeyear{1989}. The ratio, 1.87, did not match either the 6 participants who do not show any sign of scaling ($\frac{d_{200}}{d_{50}} = 1.07 \pm 0.16$) or the 2 that do ($\frac{d_{200}}{d_{50}} = 3.06 \pm 0.27$).

\subsection{Perception versus action}

We have shown that eye movements affect lateral self-motion perception and that depth compen
% Talk about whether perception and action employ different mechanisms?
% Check work by Merfeld
%
% Vestibular perception and action employ qualitatively different mechanisms I and II
% Merfeld, Park, Gianna-Pulin, Black, Wood, 2005
%
